The importance of negative alternatives in scalar implicature

### 2016-01-11 Paper/Paper.Rmd
title tweaks

---
title: "The importance of full scale representations in scalar implicature"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

>>>>

---
title: "The importance of negative alternatives in scalar implicature"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"
